---
title: "Timecourse of a Model: Autoplotting and saving as .jpeg"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE, results ='hide'}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow

Put in the path to the model (SBML), as url or local path (as string) and load the model. Use `loadModel()` for .cps models.
```{r}
modelPathSBML <- "./Models/Schaber2012SUP_model.xml"
loadSBML(modelPathSBML)
```

Set the timecourse settings. Further specifications are possible.
```{r}
setTimeCourseSettings(duration  = 50,
                      intervals = 100)
```

Where should the .jpeg image be saved?
```{r}
jpegPath <- "docs/timecourse.jpeg"
```


# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
# Check if path is already taken:
if(file.exists(jpegPath)) 
  stop("Error: This file does already exist.")

# Run time course
timecourse <- runTimeCourse()

# Autoplot time course
plot       <- autoplot.copasi_ts(timecourse)

# plot and save as pdf
jpeg(jpegPath)
print(plot)
dev.off()

```

# Output
This workflow produces the following output:
```{r}
# Show the Plot
plot
```

and saves the image in the file `r jpegPath`.