---
title: "Profile Likelihood: Hepatitis C Model"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow

Put in the path to the model (.cps), as local path (as string) and load the model. Use `loadSBML()` for sbml models.
```{r}
modelPath <- "./Models/Aston2018Breakthrough_model.cps"
model     <- loadModel(modelPath)
```

To use the results from the Sigma Point method, I will load the RDS with the results.
```{r}
SP_result <- readRDS("docs/SP_Aston")
SP_means  <- SP_result$sp_means

# set the Global Quantities to the estimated means
#setGlobalQuantities(key = getGlobalQuantities()$key, initial_value = SP_means)

# read out Variance of Global Quantities
SP_cov    <- SP_result$sp_cov_matrix
SP_var    <- c()
for (i in 1:nrow(SP_cov)){
  SP_var[i] <- SP_cov[i,i]
}

model <- getCurrentModel()
```

Load the data into the variable `data`.
```{r}
data <- read.csv("Data/Aston2018_data3.csv", sep = " ")
```

Define experiment(s) for Parameter Estimation. For multiple experiments use list of `defineExperiments()`.
```{r}
pe_experiments <- defineExperiments(
  data = data,
  type = c("time", "dependent"),
  mapping = c(NA, species("V", reference = "Concentration")),
  weight_method = "mean_square"
)
```

Set Parameter Estimation Parameters. For more parameters, copy the `defineParameterEstimationParameter()` function and append the list, or use the `make_pe_param_global()` function defined in utils and run it on the parameters you want to add.
```{r}
pe_parameters <- lapply(getGlobalQuantities()$key, make_pe_param_global, lower = 100, upper = 100)
```

Set Parameter Estimation Settings.
```{r}
pe_randomize_start_values <- FALSE
pe_update_model           <- FALSE

pe_method <- setParameterEstimationSettings(
  method = "LevenbergMarquardt"
)
```

Set Parameter for Profile Likelihood. For more parameters, copy the `defineParameterEstimationParameter()` function and append the list, or use the `make_pe_param()` function defined in utils and run it on the parameters you want to add (see above). I want to use the variance as an upper and lower bound.
```{r}
# Define beta* and p* as parameters for profile likelihood
i <- c(6,7)

for (i in i){
val <- getGlobalQuantities()$initial_value[i]
pl_parameters <- list(defineParameterEstimationParameter(
  ref         = getGlobalQuantityReferences(key = getGlobalQuantities()$key[i])$initial_value,
  start_value = val,
  lower_bound = val - 1.6*val,
  upper_bound = val + 1.6*val
))
}
```

Choose maximum number of steps for Profile Likelihood.
```{r}
max_steps     <- 50
```


Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save <- TRUE
file <- "docs/PL_Aston"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}

# Run Profile Likelihood
PL_result <- runProfileLikelihood(
  model                     = model,
  pl_parameters             = pl_parameters,
  max_steps                 = max_steps,
  pe_parameters             = pe_parameters,
  pe_experiments            = pe_experiments,
  pe_method                 = pe_method,
  pe_update_model           = pe_update_model,
  pe_randomize_start_values = pe_randomize_start_values
)

# Save results
if (save){
  saveRDS(PL_result, 
          file = file)
}
```


# Output
This workflow produces the following output:
```{r}
printLikelihoodProfile(PL_result)
```

## Utils
Creates a function for easy Parameter Estimation Parameter Usage:
```{r}
make_pe_param  <- function(name, upper, lower) {
  value_ref <- parameter_strict(name, reference = "Value")
  value     <- getValue(value_ref)
  defineParameterEstimationParameter( ref         = value_ref,
                                      start_value = value,
                                      lower_bound = abs(value)*lower,
                                      upper_bound = abs(value)*upper)
  
}

make_pe_param_global <- function(name, upper, lower){
  value     <- getGlobalQuantities(key = name)$initial_value
  value_ref <- getGlobalQuantityReferences(key = name)$initial_value
  defineParameterEstimationParameter(ref         = value_ref,
                                     start_value = value,
                                     lower_bound = value-abs(value)*lower,
                                     upper_bound = value+abs(value)*upper
                                     )
  
}

make_pe_param_global_absolute <- function(name, upper, lower){
  value     <- getGlobalQuantities(key = name)$initial_value
  value_ref <- getGlobalQuantityReferences(key = name)$initial_value
  defineParameterEstimationParameter(ref         = value_ref,
                                     start_value = value,
                                     lower_bound = value-lower,
                                     upper_bound = value+upper)
  }
```

