---
title: 'Profile Likelihood: Example Model'
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow

Put in the path to the model (SBML), as url or local path (as string) and load the model. Use `loadModel()` for .cps models.
```{r}
modelPathSBML <- "./Models/Schaber2012SUP_model.xml"
model         <- loadSBML(modelPathSBML)
```

Load the data into the variable `data`.
```{r}
data <- read.csv("./Data/Schaber2012SUP_data2", sep = ",")
```

Define experiment(s) for Parameter Estimation. For multiple experiments use list of `defineExperiments()`.
```{r}
pe_experiments <- defineExperiments(
  data          = data,
  type          = c("time", "dependent", "ignore"),
  mapping       = c(NA, "{Values[TpFit]}", NA),
  weight_method = "mean_square"
)
```

Set Parameter Estimation Parameters. For more parameters, copy the `defineParameterEstimationParameter()` function and append the list, or use the `make_pe_param()` function defined in utils and run it on the parameters you want to add.
```{r}
# pe_parameters <- list(
#  defineParameterEstimationParameter(
#   ref = "",
#   start_value = "",
#   lower_bound = "",
#   upper_bound = ""
# ))

# Or use the functions defined in utils and run it on the parameters you want to add
pe_parameters <- lapply(parameter(), make_pe_param, lower = 0.75, upper = 30)

```

Set Parameter Estimation Settings.
```{r}
pe_randomize_start_values <- FALSE
pe_update_model           <- FALSE

pe_method <- setParameterEstimationSettings(
  method = "LevenbergMarquardt"
)
```

Set Parameter for Profile Likelihood. For more parameters, copy the `defineParameterEstimationParameter()` function and append the list, or use the `make_pe_param()` function defined in utils and run it on the parameters you want to add (see above).
```{r}
pl_parameters <- lapply(parameter(), make_pe_param, lower = 0.75, upper = 30)

```

Choose maximum number of steps for Profile Likelihood.
```{r}
max_steps     <- 30
```


Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save <- TRUE
file <- "docs/PL_Schaber"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
# Run Profile Likelihood
PL_result <- runProfileLikelihood(
  model                     = model,
  pl_parameters             = pl_parameters,
  max_steps                 = max_steps,
  pe_parameters             = pe_parameters,
  pe_experiments            = pe_experiments,
  pe_method                 = pe_method,
  pe_update_model           = pe_update_model,
  pe_randomize_start_values = pe_randomize_start_values
)

# Save Result
if (save){
  saveRDS(PL_result, 
          file = file)
}

```

# Output
This workflow produces the following output:
```{r}
printLikelihoodProfile(PL_result)
```

## Utils
Creates a function for easy Parameter Estimation Parameter Usage:
```{r}
make_pe_param  <- function(name, upper, lower) {
  value_ref <- parameter_strict(name, reference = "Value")
  value     <- getValue(value_ref)
  defineParameterEstimationParameter( ref         = value_ref,
                                      start_value = value,
                                      lower_bound = value*lower,
                                      upper_bound = value*upper)
  
}
```

