---
title: "Sensitivity: Hepatitis C"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)

```
This workflow gives out the collapsed result for 4 models.

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow

Put in the path to the model (.cps), as a local path (as string) and load the model. Use `loadSBML()` for sbml models.
```{r}
# Load all models
model_PVR  <- loadModel("Models/Aston2018PVR_model.cps")
model_BT   <- loadModel("Models/Aston2018Breakthrough_model.cps")
model_Null <- loadModel("Models/Aston2018NullResponse_model.cps")
model_TriP <- loadModel("Models/Aston2018Triphasic_model.cps")

# Make a list of models
models     <- list(model_PVR, model_BT, model_Null, model_TriP)

```

Define the subtask. Has to be one of "SteadyState", "TimeSeries", "ParameterEstimation", "Optimization". 

```{r}
subtask         <- "TimeSeries"
```

Set Sensitivity Method settings.
```{r}
delta_factor    <- 0.001
delta_minimum   <- 1E-12
```

Define the effect (can be any of `r enum_effect`).
```{r}
effect          <- "NON_CONST_METAB_CONCENTRATIONS"
```

Define the cause and (if applicable) secondary cause (can be any of "SINGLE_OBJECT", "ALL_LOCAL_PARAMETER_VALUES", "ALL_PARAMETER_VALUES", "METAB_INITIAL_CONCENTRATIONS").
```{r}
cause           <- "ALL_PARAMETER_VALUES"
secondary_cause <- NULL
```

Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save           <- TRUE
file           <- "docs/Sens_Aston"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
# Set up output
result <- matrix(nrow = 8, ncol = length(models))

# Run Sensitivities for all models
for (i in 1:length(models)){
  sens_result <- runSensitivities(model           = models[[i]], 
                                  subtask         = subtask, 
                                  delta_factor    = delta_factor,
                                  delta_minimum   = delta_minimum,
                                  effect          = effect,
                                  cause           = cause,
                                  secondary_cause= secondary_cause)
  result[,i] = sens_result$main$annotated_collapsed_result
}

# Reshape data for better visualisation
rownames(result) <- rownames(sens_result$main$annotated_collapsed_result)
colnames(result) <- c("PVR", "Breakthrough", "Nullresponse", "Triphasic")

Sens_result  <- tibble(PVR  = Sens_PVR$main$annotated_collapsed_result,
                       BT   = Sens_BT$main$annotated_collapsed_result,
                       Null = Sens_Null$main$annotated_collapsed_result,
                       TriP = Sens_TriP$main$annotated_collapsed_result)


# Save file
if (save){
  saveRDS(Sens_result, 
          file = file)
}

```

# Output
This workflow produces the following output:

```{r}
result
```

