---
title: "Sigma Point: Hepatitis C Model"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow


Put in the path to the model (.cps), as local path (as string) and load the model. Use `loadSBML()` for sbml models.
```{r}
modelPath <- "./Models/Aston2018Breakthrough_model.cps"
model     <- loadModel(modelPath)
```

Load the data into the variable `data`.
```{r}
data <- read.csv("Data/Aston2018_data2.csv", sep = " ")
```

Define experiment(s) for Parameter Estimation. For multiple experiments use list of `defineExperiments()`.
```{r}
pe_experiments <- defineExperiments(
  data = data,
  type = c("time", "dependent"),
  mapping = c(NA, species("V", reference = "Concentration")),
  weight_method = "mean_square"
)
```



Use the `addParameterEstimationParameter()` function to add Parameter Estimation Parameters. Alternatively, use the `add_pe_param_global()` function defined in utils for adding global Quantities as parameters.
```{r, results='hide'}
lapply(getGlobalQuantities()$key, add_pe_param_global, lower = 100, upper = 100)

```

Set Parameter Estimation Settings.
```{r}
setParameterEstimationSettings(
  method = "LevenbergMarquardt"
)
```

Set Sigma Point Method Settings. Choose alpha, beta, kappa, and the measurement error (var)
```{r}
alpha <- 0.5
beta <- 2
kappa <- 3
measurement_error <- 0.1
```

Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save <- TRUE
file <- "docs/SP_Aston"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
# Run Sigma Point Method
result <-
  runSigmaPoint(
    alpha             = alpha,
    beta              = beta,
    kappa             = kappa,
    var               = measurement_error,
    experiments       = pe_experiments,
    mean_fit_as_basis = TRUE
  )

# Save result
if (save){
  saveRDS(result, 
          file = file)
}
```

# Output
This workflow produces the following output:
```{r}
result$sp_mean
result$sp_cov_matrix
```
## Utils
Creates a function for easy Parameter Estimation Parameter Usage:
```{r}
make_pe_param  <- function(name, upper, lower) {
  value_ref <- parameter_strict(name, reference = "Value")
  value     <- getValue(value_ref)
  defineParameterEstimationParameter( ref         = value_ref,
                                      start_value = value,
                                      lower_bound = value*lower,
                                      upper_bound = value*upper)
  
}

make_pe_param_global <- function(name, upper, lower){
  value     <- getGlobalQuantities(key = name)$initial_value
  value_ref <- getGlobalQuantityReferences(key = name)$initial_value
  defineParameterEstimationParameter(ref         = value_ref,
                                     start_value = value,
                                     lower_bound = value-value*lower,
                                     upper_bound = value+value*upper)
}

add_pe_param_global <- function(name, upper, lower){
  value     <- getGlobalQuantities(key = name)$initial_value
  value_ref <- getGlobalQuantityReferences(key = name)$initial_value
  addParameterEstimationParameter(   ref         = value_ref,
                                     start_value = value,
                                     lower_bound = value-value*lower,
                                     upper_bound = value+value*upper)
}
```
