---
title: "Sigma Point: Example Model"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow


Put in the path to the model (SBML), as url or local path (as string) and load the model. Use `loadModel()` for .cps models.
```{r}
modelPathSBML <- "./Models/Schaber2012SUP_model.xml"
loadSBML(modelPathSBML)
```

Load the data into the variable `data`.
```{r}
data <- read.csv("./Data/Schaber2012SUP_data2", sep = ",")
```

Define experiment(s) for Parameter Estimation. For multiple experiments use list of `defineExperiments()`.
```{r}
experiment <- defineExperiments(
  data          = data,
  type          = c("time", "dependent", "ignore"),
  mapping       = c(NA, "{Values[TpFit]}", NA),
  weight_method = "mean_square"
)
```



Set Parameter Estimation Parameters. For more parameters, copy the `defineParameterEstimationParameter()` function and append the list.
```{r}
addParameterEstimationParameter(
    ref = "{(T -> Tp; S).k}",
    start_value = 0.1,
    lower_bound = 0,
    upper_bound = 100)


addParameterEstimationParameter(
    ref = "{(Tp -> T).k1}",
    start_value = 0.1,
    lower_bound = 0,
    upper_bound = 100)

```

Set Parameter Estimation Settings.
```{r}
setParameterEstimationSettings(
  method = "LevenbergMarquardt"
)
```

Set Sigma Point Method Settings. Choose alpha, beta, kappa, and the measurement error (var)
```{r}
alpha <- 0.5
beta <- 2
kappa <- 3
measurement_error <- 0.1
```

Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save <- TRUE
file <- "docs/SP_Schaber"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
# Run Sigma Point Method
result <-
  runSigmaPoint(
    alpha             = alpha,
    beta              = beta,
    kappa             = kappa,
    var               = measurement_error,
    experiments       = experiment,
    mean_fit_as_basis = TRUE
  )

# Save Result
if (save){
  saveRDS(result, 
          file = file)
}
```

# Output
This workflow produces the following output:
```{r}
result$sp_mean
result$sp_cov_matrix
```

