---
title: "Sensitivity: Example Model"
author: "Johanna Daas"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8,
  fig.asp = 10/16,
  out.width = "100%",
  error = TRUE,
  warning = FALSE,
  message = FALSE
)
set.seed(1)
```

# Setup
First, load the libraries needed for the workflow
```{r,  message = FALSE}
library(tidyverse)
library(CoRC)
```

# Input
Put in all variables needed to customise the workflow

Put in the path to the model (SBML), as url or local path (as string) and load the model. Use `loadModel()` for .cps models.
```{r}
modelPathSBML   <- "./Models/Schaber2012SUP_model.xml"
model           <- loadSBML(modelPathSBML)
```

Define the subtask. Has to be one of "SteadyState", "TimeSeries", "ParameterEstimation", "Optimization". 

```{r}
subtask         <- "SteadyState"
```

Set Sensitivity Method settings.
```{r}
delta_factor    <- 0.001
delta_minimum   <- 1E-12
```

Define the effect (can be any of `r enum_effect`).
```{r}
effect          <- "NON_CONST_METAB_CONCENTRATIONS"
```

Define the cause and (if applicable) secondary cause (can be any of "SINGLE_OBJECT", "ALL_LOCAL_PARAMETER_VALUES", "ALL_PARAMETER_VALUES", "METAB_INITIAL_CONCENTRATIONS").
```{r}
cause           <- "ALL_PARAMETER_VALUES"
secondary_cause <- NULL
```

Do you want to save the result as a RDS object? Also give the file, where you want to save it.
```{r}
save           <- TRUE
file           <- "Sens_Schaber"
```

# Workflow
This should generally not need to be changed, only if the workflow is to be changed more generally.
```{r}
Sens_result <- runSensitivities(model           = model, 
                                subtask         = subtask, 
                                delta_factor    = delta_factor,
                                delta_minimum   = delta_minimum,
                                effect          = effect,
                                cause           = cause,
                                secondary_cause = secondary_cause)

if (save){
  saveRDS(Sens_result, 
          file = file)
}

```

# Output
This workflow produces the following output:

 Result:
```{r}
Sens_result$main$annotated_result
```

Scaled  Result:
```{r}
Sens_result$main$annotated_scaled_result
```

Collapsed Result:
```{r}
Sens_result$main$annotated_collapsed_result
```

